% !TeX spellcheck = en_GB
% !TeX root = Report.tex
\phantomsection
\addcontentsline{toc}{section}{Appendix 5 - Notes from Invited Presentations}
\sect{5. Notes from Invited Presentations} \label{Notes}
These notes are raw and not altered in any way from when they were taken from the invited presentation. These notes have been distilled and focussed through the lens of our report title and hypothesis to the content shown in section 1.

\subsect{Lecture 1 - Fabrice Perrot - Managing Director Alstom Grid Research and Technology Centre}
Alstom 130 years old. 
Emerged from General Electric Company in the UK. 
Alstom made up of four sectors; thermal power, transport, renewable power and grid. 
All four sectors are present in the UK. 
Alstom Grid section based in Stafford. 
Power transformers are built at a large factory in Stafford. 
They also make HVDC transformers there. 
Instrument transformers, circuit breakers and disconnectors and gas insulated substations (GIS) are also manufactured and design within Alstom Grid but not necessarily at Stafford. 
In Stafford the R\&D for HVDC power electronics and offshore substations are investigated. 
They also design substation automation solutions or relays and controls as it used to be called.

5 research and development centres with 4\% of Alstom sales being reinvested in Alstom Grid R\&D. 
1200 skilled engineers working on R\&D challenges including HVDC, UHVDC and Smart Grid techniques. 
Experts in final element modelling and have developed their own unique software for FEM calculations.
The core competency of Alstom Grid is in High Voltage and Dielectric Materials. 
They are experts in developing materials that are largely non-porous to prevent voids. 
Glass fibre materials are an example of this. 
This helps to avoid partial discharge in the material which can eventually lead to breakdown. 
Some of these materials are employed in different industries and settings, such as the Eurostar, T45 Destroyers and the Astute Submarines. 
The applications of this research are quite wide ranging.

Funding is also taken on collaborative projects from the public purse. 
The EU HORIZON 2020 policy is one such source of funding for HV research. 
The technology strategy board funds ``catapults'' to try and deploy innovation as a product. 
National Grid, Scottish Power and Scottish and Southern Electric are transmition system operators that can gain access to funding through Ofgem and a new funding system called RIIO - Revenue = Incentives + Innovation + Output. 
The RIIO is comprised of the Network Innovation Allowance, Network Innovation Competitions and the Low Carbon Network Fund. 
These are just some of the levers available.

\textbf{Energy Policy}
80\% reduction of 1990 CO2 levels by 2050 and 34\% by 2022. 
Renewables to supply 15\% of UK energy by 2020.
 UK achieves about 3\% currently. 
This is not a very long time in the power industry. 
Road transport and energy efficiency is important. 
The energy trilemma is key - security, economics and emissions. 
The Climate Change Act 2008 and the Energy Act 2008 are key with chapters 27 and 32 respectively being the chapters with the figures in them.

In order for this to take place, the complexity of the distribution network must increase. 
Energy world consumption is likely to increase by 50\% between 2007 to 2035. 
A huge increase in renewables is required while a huge reduction in the very large fossil fuel powered stations.

One of the European wide strategies is increased interconnection. 
There are vast renewable resources, including huge amounts of wind in the North Sea, Hydro in Norway and a massive amount of thermal solar in the North of Africa. 
The distances involved are very large, with thousands of kilometres from the renewable concentrates to the load centres. 
One of the ways of distributing this power is through HVDC rather than the AC networks currently prevalent throughout distribution. 
Clearly there are large technical challenges and massive political challenges in dealing with instability in North Africa for the Solar. 

The wind however is a different story. 
The distances can be up to 3000km, which AC transmission would simply not be cost effective. 
There are numerous plans to start harnessing North Sea power and there are a few already in deployment. 
These projects are very capital intensive - 100 millions of euros and can cost Alstom dearly if the small weather window is missed to deploy the technology.

\textbf{Why Do We Need HVDC?}

Thomas Edison proposed DC and George Westinghouse proposed AC. 
Westinghouse won due to the difficulties with DC. 
Transformers for DC do not exist and made it very difficult to step up the voltage for long distance transmission. 
For HVDC, you start with an AC power source and put it through a big rectifier bridge. 
Then you transmit the HVDC power over the cables, then you change it back to AC at the other end. 

Several types of link exist. 
Back to back links allow asynchronous connection, allowing 50Hz and 60Hz networks to be connected. 
Point to Point is the same but has an Over Head Line (OHL) for bulk transmission over distance. 
Point to Point schemes also exist in submarine versions, where the cable is subsea and this is used for the connection of wind farms in the North Sea. 
AC power is continuously charging and discharging the capacitive impedance in the cable, resulting in large reactive power consumption. 
The DC version only charges the impedance once (like a resistance) so the consumption is much less over long distances. 
The HVDC scheme between France and the UK was extremely successful, it paid for itself in just 3 years and achieves over 97\% availability. 

Another aspect of AC is space. 
AC for a double circuit would require six large cables - requiring a big tunnel for heat dissipation. 
DC requires only one for a monopolar link or two for a bipolar link, thus saving space. 
DC cables also produce less heat.
AC systems require reactive compensation in the form of FACTS (Flexible AC Transmission System) over long distances. 
Even though DC converter stations cost alot of money, they do not require periodic compensation. 
Thus over a very long distances, there is a distance break-even point where HVDC becomes cheaper than AC. 
This is around 30 miles for underground or submarine systems and around 500 miles for OHLs.

The power rectifier is usually a 12 pulse connection. 
This is a six pulse grid connection utilising 6 thyristors to produce a DC voltage. 
You can put two six pulse bridges together to produce a twelve pulse bridge to allow more power to be put in the system. 
You can then add two of these twelve pulse bridges together, to allow one for V+ and one for V-. 
In China these run at +\-800kV and allow 5000-6000 MW to be transmitted down just two wires. 
This is a huge amount of power.

The key technology is thyristor technology that enables this HVDC connection. 
A huge amount of technology is invested in these systems. 
There are also VSCs (Voltage Source Converters) which are a series of capacitors in series with the AC, and a set of insulated gate transistors (IGCT) which switch the capacitors in and out. 
These are called multi-level converters. 
This technology is very useful for renewable energy connection.

Thyristor valves are usually arranged in quadrivalves. 
The Alstom H400 valve modules provide two stacks of thyristors in series. 
These are watercooled. 
Thyristor technology is interesting because they fail short circuit. 
So they build in redundancy.
 Every two years, the HVDC system undergoes maintenance. 
Each H400 module is arranged in fours to make a quadrivalve and then there are six of these in a twelve pulse bridge. 
These are suspended from the ceiling for seismic reasons.

In early 2000s, HVDC was largely a curiosity. 
In China and other large countries, there was a huge renaissance in HVDC technology. 
800kV is the standard voltage for HVDC in China. 
India is building it's first 800kV HVDC scheme, although it is only 2.5GW capacity compared to the huge ones in China. 
In the late 80s, the Brazillian Itaupu Hydro dam was the highest voltage introduced by ABB at 600kV. 
In China they are starting to think about +\-1.1MV. 
Although Fabrice thinks this is probably uneconomic.

One of the highest power schemes was in China. 
The Ningdong-Shandong +\-660kV scgene was built. 
It is the world's largest single power electronic converter at 2GW. 
4 converters in total, 2 at each end. It was built in pairs of valves not in quadrivalves. 

These were all tested in the lab at full scale before deployment. 
These are very big pieces of kit. 
The HVDC centre of excellence in Stafford produced a very large power transformer suitable for these huge amounts of power.

A Line Commutated Current HVDC station at Chandrapur 2x500MW back to back station in India has a small building to house the thyristors, but 440mx530m is required to filter the high frequency harmonics from the system.

\textbf{Nanotechnology}
Advantages available for both AC and DC technologies. 
Cigre D1-40 WG Functional Nanomaterials for Electric Power Industry was a technical brochure published at the end of 2013. 
Nanotechnology could improve the performance of dielectrics massively, increasing safety and economics. 

There is an issue understanding how the dispersion of micro and nano fillers act within epoxy matrices. 
We need to understand how to make reproducible materials and try to understand how this works and what benefits can be offered.
 An important research area is the improvement of thermal conductivity while maintaining electrical resistivity. 

If thermal conductivity can be increased by a factor, then the size of equipment can be vastly reduced. 
Diamond is the example of this is nature. 
It has very good thermal conductivity while remaining electrically insulative. 
Boron Nitride is another interesting material that could be a candidate to improve dielectric strength while improving thermal conductivity.

Epoxy-Alumina nanocomposites show promise in resisting surface discharge.
 Often pollution and impurities and imperfections in the insulating material can cause partial discharge in the form of surface discharge. 
The 3\% nano filler material can resist surface discharge for extreme periods.

The Technology Strategy Board funds the Alstom project, NanocompEIM. 
Around 20 engineers working together. 
It costs around a million euro for 30 months, and about half of it is covered by the TSB. 
They are tackling the increased dielectric strength while increasing thermal conductivity problem. 
Today they can make small quantities of nano-materials, but they are trying to develop ways to mass manufacture when proven. 
The upscale is the objective of the project. 
The TSB require reporting and a focus on the deployment and demonstration of the technology.

\textbf{The BIG Multi Disciplinary Challenge}
A huge amount of innovation is required to meet the energy challenge in all engineering disciplines. 
Mechnicals, electronics, controls\dots there is loads of opportunities. 
A huge amount of investment is required.
 The Government is setting out more provision for these types of challenges to be met.
Will we see the planned expansion in HVDC multi-terminals systems in Europe in our lifetime?

\textbf{Questions}
What currents do you transmit at? The issue with DC is that the current never goes through zero, so the magnitude is not the problem, it is the fact it is not cyclic. Multi-
terminal systems require very quick acting circuit breakers. The DC current for the Chinese projects was around 4000-5000 amps. This pushes all the connections as far as possible (6250A is around the maximum). DC is perhaps more dangerous as DC burns 
you while AC stops your heart - which is worse?!?

Are the 20:20:20 goals realistic? What are the financial motives in a private market? We need to achieve it - the consequences of climate change could be catastrophic. The finance is a huge issue. The economic climate is a big issue. Huge investment is required. We need investment banks to be more positive.If you removed the subsidies from EU and government policies, would Alstom or any other power equipment manufacturer be profitable? The financing of the R\&D is an issue for governments. These require the finding mechanisms from government. The large HVDC schemes are commercial entities, and alot of money can be made in the private market for new transmission systems. You need to spend money as a company in innovation to continue profitability. These funding schemes are important to providing that lifeline. These could be viewed more as a stimulus, the Horizon 2020 schemes is of the order 70 billion euro. It is quite important therefore that these continue, but perhaps this is since electricity is vital, if intel's chip R\&D halted, we would probably be OK for a short while.

What about integrating micro generation in the grid and how invested is Alstom in meeting government targets? Innovation is required throughout the industry. Even in AC, work is undertaken to leakproof SF6 systems and ultimately to find a non-greenhouse effect insulating Gas. Also mineral oil coolant for transformers contaminates the ground in the event of a leak, and burns in an accident. Research into vegetable oil coolants could be useful if regulations change to disallow or penalise mineral oils (or SF6 mentioned prior). There is a huge amount of innovation required and Alstom is constantly trying to stay one step ahead of the crowd.
\subsect{Lecture 2 - Tim Whitcher - Capbrown Management Consultancy}

Taking a big picture view of an engineering project. There are technologists with a primarily technical focus and requires detailed in-depth knowledge. The delivery tasks focus on project management. The systems roles take a broader high level views. Often the backbone of major projects and the interface between engineers and managers. Finally Management as in the conventional manager. These are parallel tasks. Often modern organizations are matrix organizations - you can move between the four tasks freely to some extent. Some people naturally fall at one end of the parallel tasks.

Consider the exploitation of technology. An R\&D project requires a huge amount of consideration. Who is the target market? Stakeholders? Technical Limitations? Market Conditions? Future Proof? Shipping? Sustainability? Export and Import Fees? Local Distribution? Is the product sufficiently viable to let all these things happen? Do you know your markets well enough and think out of the box with applications of your technology?

From R\&D you go to delivering the product in an industrial setting. The exploitation of technology takes much more than just the technology. Project skills are really important to deliver that technology to market in order to profit.

Think about Gooch and the railways. He had to build the locomotive sheds to build trains for great western. He built the sheds at swindon as they are equidistant. As the bird flies its not - Bristol is 50 miles and London is 70 miles. However due to the different trans used, Swindon is exactly band in the middle of the number of wheel rotations required. Think out of the box - solve some big problems.

Capbrown consulting. Get on linked in and start networking. Start following companies that are interesting. Free subscriptions to havard business review, careerealism and MIT Sloan Management Review. 7 seconds to read a CV - Same for a report!

Capbrown are a consultancy and they are mostly ex rail professionals. Most of their work is with rail companies. They are an international company, working in Melbourne at some points. Jubilee and Northern line upgrade. TFl traffic management system. Vic upline and district line and reading with Siemens. 

\subsect{Lecture 3 - Introduction to Standards and Standardization - Dr Peter Hatto, Head of R\&D, Ionbond UK Ltd}
\label{sec:lect3}
Previous chairman for various ISO technical committees for nanotechnology including ISO/TC 229, CEN/TC 352 and BSI/NTI/1. 
Governor of ISO/TC 206/WG10 for ceramic coatings and for CEN/TC 184 for Test methods for Ceramic Coatings.

Two types of standards; metrological like mass length and time and Documentary standards which are more usually what we mean by talking about standards. 
Standards provide agreed ways of naming, describing and specifying things. 
It also specifies test procedures and how we manage and report things ISO9001 and ISO14000. 
Standards can be normative - they tell you what must be done in order to comply with the standard, or informative which provide information only. 
Standards are usually a mixture of both, and usually contain annexes or appendices that are both. 
Standard compliance are VOLUNTARY unless agreed to in a contract or referred to in regulation. 
Standards are based on consensus not necessarily unanimity. 
The process of development is voluntary. 

The definition of a standard - \textit{A document, established by consensus and approved by a recognized body, that provides, for common and repeated use, rules, guideline or characteristics for activities or their results, aimed at the achievement of the optimum degree of order in a given context}.
 From the ISO/IEC Guide 2:2004 definition 3.2. 
Standards promote a uniform approach, and will be open source.

Standards often cost money to buy the document. 
These are to cover the cost of creating the standard. 
The open source document ensures safety, quality and reliability of products, processes and services, efficient production, cost reduction through competition and support regulation. 
They allow you to disseminate knowledge and use new processes and procedures. 

Standards are not essential to life, but absolutely essential to modern living. 
They are ubiquitous and cover everything from shoe sizes, nuts and bolts, petrol grades, warning signs, pipes and fittings, fire extinguishers, gas cylinders, shipping containers. 
There are some 20,000+ international standards. 
They work very efficiently, so much so that they are virtually invisible to ``the man in the street''. Internet protocol and aircraft fuel are another two examples that were discussed. 
There are around 570 ISO standards that apply to road vehicles, plus ISO 3779 which covers vehicle identification numbers. ISO 3591 is a standard for wine glasses. 
ISO 9564 is a standard for financial services such as PINs. ISO 10002 is for quality management for customer satisfaction.

An example of standards that apply in everyday life is in a car tyre puncture. 
ISO 4000-1 gives a standard for passenger car tires, and ISO 4000-2 gives the standard for rims. 
This means as long as you comply with those standards, you can confidently use a replacement from any manufacturer. 
There is a huge amount more standards relating to the safety and quality of petrol pumps, including the pump station, the fuel nozzle and the performance of the fuel. 
Credit cards are another example, with standards specifying their size, the IC design and the card reader.

Standards can be formal that is they are developed by independent experts working under the auspices of National, Regional or International standards body. 
National standards bodies include:
\begin{itemize}
\item \textbf{AFNOR} - France, 
\item \textbf{BSI} - Britain, 
\item \textbf{DIN} - Germany, 
\item \textbf{JIS} - Japan. 
\end{itemize}
Regional institutes include:
\begin{itemize}
\item CEN, 
\item CENELEC, 
\item ETSI. 
\end{itemize}
International bodies include:
\begin{itemize}
\item ISO, 
\item IEC,
\item  ITU. 
\end{itemize}
Standards can be adopted between these organizations or shared. 
There are also informal standards created by SDOs - standards development organizations. 
These include the ASTM, IEEE, SAE, SEMI, VDI. 
There are around 600 of these particularly prevalent in the US. 
Private standards can be developed by a company or trade association such as ZigBee.
 Formal standards are proposed, developed and approved by the members of the standards body or an accredited organization. 
These are based on consensus - no sustained opposition - not unanimity. 
Standards development couple the needs of stakeholders to available solutions. 
Standards should have a purpose, which is usually developed through pre-normative research and co-normative research.

The functions of standards are primarily to provide 4 things. 
Interoperability/Compatibility as with nuts and bolts, rail gauges plugs and outlets etc. 
Quality - to ensure fitness for purposes or safety. 
Variety reduction/optimization for example shoe sizes or suit sizes to allow mass production and price reduction. 
Information/Measurement gives tests and measurement methods for describing, quantifying and evaluating product attributes such as material, processes and functions.

DIN - the German national standards organization - report that in Europe, standardization adds around 1\% to the value of GDP and that the value added generated by standardization is at least as valuable as patents. 

Standards and regulation are distinctly different. Nicholas Chamfort, a French philosopher said ``it is easier to legislate than to legitimize''. 
Regulations are based on legislation to meet a societal imperative for example speed limits or drug laws. 
These are affected by objective evidence and political expediency. 
With regulations, there must also be robust measurement and testing to enforce these regulations, provided by a standard. 
Formal standards demonstrate legitimacy since they are derived from an expert community to provide a benchmark. 
They are based on objective and verifiable requirements and the process is robust, transparent, consensual and voluntary. 
If people use a standard voluntarily, then it demonstrates a certain level of legitimacy. 
They can provide a basis for demonstrating compliance (EC new approach directives are an example).

Standardize or patenting? 
Standards represent agreement between experts on the optimal approach and do not require an inventive step but represent best practice. 
Adoption of a standard should support efficiency and overall cost reduction. 
The costs of a standard should be relatively low. 

Patents are for protecting the IP of an inventor and to limit the scope of competitors to gain access to the market. 
The cost of obtaining, maintaining and defending a patent can be considerable. 
Patents require inventive steps to be obtained. 
The question to ask for any new technology is ``is there an inventive step?'', ``what is the commercial potential and is it sufficient to offset the cost of patenting?'' and ``What is the lifetime of the invention?''

International Organization for Standardization - ISO. It is a global, inclusive, democratic and member driven organization. The USA has the same power as Sri-Lanka or other countries, one vote each. Standards are proposed by ISO members, developed by experts nominated by members and are voluntary. They provide critical elements of soft governance such as ISO 9001 and ISO14001. 

Why do we need CEN then if we have ISO? 
CEN is for the European market with a special focus on the EU market. 
To build a single market and therefore larger markets means more wealth. 
This provides interesting issues with the recent EU-USA trade agreement negotiations.
 Every member of the EU adopts all of the CEN standards, and conflicting national standards are being resolved. 
There are more than 500m customers throughout Europe. 
This is a significant market. 

Standards are developed in working groups (WGs), Technical Committees (TCs), and Subcommittees (SC) responsible for certain areas of standardization. 
Horizontal committees develop standards that provide underpinning support to all areas, such as quality management and assurance etc. 
There are vertical committees to develop standards relevant to specific sectors. 
Within CEN almost all of them are vertical committees focused on specific areas. 
CEN and ISO often work closely due to the largeness of CEN.

There are 3 principle deliverables from ISO and CEN.
 International Standard IS/European Norm EN - Technical Specification TS - Technical Report TR. 
They take less time to formalize as you go down the list.

No country is obliged to accept ISO standards whereas all members of CEN undertake to adopt all EN as national standards (BS-EN or DIN-EN). 
ISO standards can be adopted as ENs through unique acceptance procedures to essentially fast track this to adoption, although not all ISO standards become ENs.

Membership of ISO technical committees includes participating members, observer members and liaison members. 
Only the participating members vote on the adoption of the standard. 
The nanotechnology standard had around 34 participating members from a variety of nationalities.
 There were about 10 observer members and 20 liaison members. 
The technical committee itself is governed by a Chairman and Secretary and there are usually segmentation into working groups of sub-committees that focus on specific issues relevant to the standard area. 
The working groups generate most of the actual content of the standards. 
Working groups are usually divided into project groups as well.

Standards go through four stages. 
A proposal stage is where a member requests a new standard due to a requirement for their stakeholder. 
The committee decides whether to develop the standard which requires a minimum of 5 participating members to support it. 
At the project stage, they go away and develop the standard. 
The final draft of the document is sent out to the membership of the committee for enquiry.
 The approval stage is where it is sent out to all members of ISO and balloted by the full membership. 
The aim at all stages is to reach a consensus. 
This takes about 3 months for proposal, a year in the project stage, a year in enquiry and a year in the approval stage. 
This is now getting much quicker due to electronic delivery. 
This formulation of a standard is itself covered by ISO/EN directives.

Companies have been developed to audit procedures to certificate compliance with standards. 
Lloyds Register is one such company. 
Companies are often complying with ISO9001, ISO14001 and OHSAS 18001. 
SGS is another company that is accredited to provide certification. 




