%  Appendix_Contributions.tex
%  Document created by seblovett on seblovett-Ubuntu
%  Date created: Sun 16 Feb 2014 09:27:55 GMT
%  <+Last Edited: Sat 22 Mar 2014 13:39:37 GMT by seblovett on seblovett-Ubuntu +>
% !TeX spellcheck = en_GB
% !TeX root = Report.tex

\phantomsection
\addcontentsline{toc}{section}{Appendix 1 - Team Contributions}
\textbf{\uppercase{Appendix}} \par
\sect{1. Team Contributions}

Note that for each report there will be a different chair person.
The chair person is expected to lead the report writing process, including ultimate decision on topic, the allocation of research and the collation of content provided by others. 
Hence it is expected that one team member contribute more per report, thus averaging out over all three reports for the module.
The contribution to the module as a whole will be approximately even from each team member.

\begin{center}
\begin{longtable}{|>{\raggedright\arraybackslash}m{0.2\textwidth} | m{0.75\textwidth} |} \hline
\textbf{Team Member} & \textbf{Contribution} \\ \hline
\endhead
\texorpdfstring{\href{mailto:tjs1g10@ecs.soton.ac.uk}{Thomas J. Smith}}{Thomas J. Smith} 23914254 & Lecture 1 and Nest case study sections. Cheif of figures. Full lecture notes appendix.  \\ \hline
\texorpdfstring{\href{mailto:hl13g10@ecs.soton.ac.uk}{Henry S. Lovett}}{Henry S. Lovett} 23900091 & Chairperson for this report.  Atmel case study, lecture 2, introduction and conclusion. \\ \hline
\texorpdfstring{\href{mailto:ajr2g10@ecs.soton.ac.uk}{Ashley J. Robinson}}{Ashley J. Robinson} 24008346 & Iridium and lecture 3 sections. \\ \hline
\end{longtable}
\end{center}
%\inote{AJR and HSL fill in your student number - Done}

