% !TeX spellcheck = en_GB
% !TeX root = Report.tex
\phantomsection
\addcontentsline{toc}{subsection}{Case 1 - Transport for London: Crossrail Ltd}
\subsect{Case 1 - Businesses connected to Crossrail Ltd}

Crossrail Ltd (CRL) is a subsidiary of TfL.
Originally a joint venture with the Department for Transport (DfT) their goal is to develop transport links throughout the South East and secure London's financial excellence in Europe~\cite{crossrail:about}.
In February $2005$ CRL proposed the \emph{Crossrail Bill} which became the \emph{Crossrail Act} in July $2008$.
This supports construction of a ``railway transport system running from Maidenhead\dots and Heathrow Airport\dots through central London to Shenfield''~\cite{crossrail:act}.
As the largest civil engineering project in Europe CRL has awarded direct contracts worth upto \pounds $5.5$bn benefiting over $17,000$ businesses~\cite{crossrail:suppliers}.
In this group of small enterprises and large companies which have benefited most and did they adapt their business model specifically to allign with governance?  

In February $2014$ a Canadian company Bombardier Inc. won a \pounds $1$bn contract, over Hitachi, to deliver and maintain $65$ new trains and a depot for the line~\cite{bbc:bombardier,tfl:bombardier}.  
Bombardier has been providing mass transit solutions since $1974$ and growing steadily since so this opportunity is part of their core competence~\cite{bombardier:about}.
The company owns a passenger rolling stock plant in Derby and in $2011$ cut over a third of staff there as they failed to win a contract for the Thameslink service over Siemens~\cite{tele}.
At this point the entire future of the plant and $1,400$ jobs in Derby lay on securing the contract for the Crossrail project.

PODFather is a company that manufacture rugged handheld devices for use in logistics, earthworks and field services.
In March $2013$ the company revealed CRL is using ``PODFather for Field Force capture of Vehicle Bookings data''~\cite{podfather:crl}.
CRL is just one of their many customers which includes large enterprises such as Alstom.
This contract win can be traced to an excellent product and them being based in the UK.


CRL estimates they have provided a \pounds $42$bn benefit to the construction industry in the UK.
This benefit to businesses is down to the government objective to recycle money in in the local economy.
It is therefore a great time to be an earthworks/train company based in UK; even more so with High Speed 2 (HS2) project on the horizon.

