% !TeX spellcheck = en_GB
% !TeX root = Report.tex
\phantomsection
\addcontentsline{toc}{subsection}{Iridium}
\subsect{Iridium}

In $1998$ Iridium, a company that spun out of Motorola in $1991$, launched their telecommunications service to the public.
In $1999$ Iridium filed for bankruptcy~\cite{fink2000iridium}.%\citeneeded.
The company started a ground breaking Low Earth Orbiting (LEO) satellite network which was made possible by a total \$$5$ billion (USD) investment from Motorola.
Expanding on existing mobile phone technology by offering global connections without delays.
Satellite technology is extremely complex and the seven years before release was spent designing, constructing and launching the network~\cite{fink2000iridium}. 
It is widely agreed that the failure of the company can be attributed to the expensive handsets and call tariffs.
Initially they managed to attract less than half the number of expected customers and these fell quickly as issues with the handsets arose~\cite{bill1999}.


Iridium holds over one thousand patents; two of which are key and based around the original idea which was conceived by three engineers~\cite{ip2010,bertiger1995satellite,bertiger1997satellite}.
This aggressive patenting strategy evidently did not protect the company from failure and the argument can be made that patents were redundant in their approach.
The concept was, and in fact still is, on the very crest of the technology wave and required a very large amount of backing to implement.
Why patent in this situation?
Patenting provides very little to the business drawing time and money away from other sections however the cost and time to process patents is insignificant in this grand business model context.


Iridium has made a comeback since this fatal chain of events and currently working to upgrade the network under the new brand Iridium NEXT~\cite{iridiumNEXT}.
Resolving their previous issues by aiming services at industries, such as maritime and oil, that can make far better use of a truly global network~\cite{better2009}.
It can be argued that the large number of patents assisted Iridum when making a return.  

\todo[inline]{Iridium needs completing}
\todo[inline]{Is failure linked to the large amount of patents?}
\todo[inline]{I think a better structure is: Intro to company (what they did); Patent strategy; Success Fail; Conclude stating if the patent strategy is linked to success/failure}
