%  Introduction.tex
%  Document created by seblovett on seblovett-Ubuntu
%  Date created: Sun 16 Feb 2014 09:18:38 GMT
%  <+Last Edited: Sun 09 Mar 2014 10:51:09 GMT by seblovett on seblovett-Ubuntu +>
\phantomsection
\addcontentsline{toc}{section}{Introduction}
\sect{Introduction}

\inote{Needs some neatening and completing. More references! Definition of terms done}

Starting a company is a very difficult task to undertake. 
There is much discussion as to the strategy that should be taken in order to make the company successful \cite{}.
In this report, an emerging company is one which has been around for eight years or less \cite{zahra1996technology}. 
An emerging company is deemed successful if it then becomes an established company after the 8 year mark.
An established company is one where the company has developed a product range for a specific market \cite{kekale2007successful}.
It can also be successful if it is acquired by and/or merged into an established company. 

\inote{Discussion of patents, how to acquire, costs, why, benefits, drawbacks\dots Should fill the rest of the intro}

In \cite{zahra1996technology}, a six stage plan for an emerging company is discussed. 
Although this is aimed at the biotechnology industry, the strategy still applies to other areas. 
The later parts of the strategy concern the research and development, and in particular, the acquisition of patents. 
This report aims to investigate whether the early acquisition of patents leads to the success of an emerging company.

The report is spit into three sections. 
The first discusses material from the invited talks, with thought to the report's hypothesis.
The second documents a number of case studies investigating the hypothesis.
The final section then concludes the report.
