%% ----------------------------------------------------------------
%% Specification.tex
%% ---------------------------------------------------------------- 
\documentclass{elec6049Report}     % Use the Article Style
%\usepackage{cite}            % Use Natbib style for the refs.
\removecolourlinks    % Uncomment this command to remove colour from any links
%% ----------------------------------------------------------------
%\usepackage[disable]{todonotes}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{multirow}
\newcommand{\inote}[1] {\todo[inline]{#1}}
\newcommand{\citeneeded}{\cite{NEEDED}\todo[color=green!40]{Citation needed}}
\usepackage{lipsum}
% sets TexCount to ignore inotes
%TC:macro \inote 1
%TC:macro \sect [2]
%TC:macro \subsect [2]
\begin{document}
%TC:ignore
\frontmatter
\reportnumber{2}
\title      {How Does Technology Make Money? - Emerging Companies}
\thetitle   {How Does Technology Make Money? - Emerging Companies}%hacks to get it in the footer
\authors    {
\texorpdfstring{\href{mailto:hl13g10@ecs.soton.ac.uk}{Henry S. Lovett}}{Henry S. Lovett},
\texorpdfstring{\href{mailto:ajr2g10@ecs.soton.ac.uk}{Ashley J. Robinson}}{Ashley J. Robinson},
\texorpdfstring{\href{mailto:tjs1g10@ecs.soton.ac.uk}{Thomas J. Smith}}{Thomas J. Smith}}

\groupnumber{14}
\maketitle
%TC:endignore
%TC:break Abstract
\listoftodos
\phantomsection
\addcontentsline{toc}{section}{Abstract}
\begin{abstract}
This report investigates whether the acquisition of patents is important to an emerging company. 
Notes from the invited seminars are included along with extra reasearch into related companies.
Three case studies are done in more depth on three companies - Atmel Technologies Ltd., Nest and Iridium.
It is shown that patents are valuable assets to a company, but they are only particularly useful for an emerging company when it is the first to market.
Being first to market and holding patents on the product creates a monopoly for the patent holder to become successful with very little competition.
Other than this, patents tend not to be worth while for an emerging company due to the costs involved.
\end{abstract}
%TC:break _main_
\mainmatter
\input{Introduction}
\input{Section1}
\input{Section2}
\input{Conclusion}

\backmatter
%\inote{The references so far do not follow the required format. See the word document for the required format. I'm not sure exactly what format it is but it has more information than currently}
\bibliographystyle{unsrt}%{ieeetr}
\bibliography{ReportBib}

\appendix
%TC:ignore
\input{Appendix_Contributions}
\input{Appendix_Minutes}
%\clearpage
\input{Appendix_LectureNotes}
%\clearpage
%TC:endignore
 
\end{document}
